### 2021-03-12 ch/6-discussion.tex
Add one and a half additional sentences

\chapter{Discussion and future work}\label{ch:conclusion}
In this thesis, I have presented three approaches for dealing with dataset bias.
The first one deals with a form of label bias and the other two with forms of sampling bias.
While this by no means covers \emph{all} possible biases,
it contributes to a growing literature that tries to tackle this problem.
One could ask if there is one method that is able to cover all possible dataset biases,
but I think there is a strong argument to be made that no general method can exist,
because it is, \eg, not possible to describe in general what is spurious information and what is relevant information.
Nevertheless, finding methods that are more generally applicable is a worthy goal.

>>>>

\chapter{Discussion and future work}\label{ch:conclusion}
In this thesis, I have presented three approaches for dealing with dataset bias.
The first one deals with a form of label bias and the other two with forms of sampling bias;
in both cases the bias is linked to a special attribute \(s\) of the data.
%
% mention again the main strengths of the presented methods
%
The first approach used knowledge of general statistics of the ``fair'' data distribution to offer a quite general method for correcting label bias,
that is intuitive to tune.

While this by no means covers \emph{all} possible biases,
it contributes to a growing literature that tries to tackle this problem.
One could ask if there is one method that is able to cover all possible dataset biases,
but I think there is a strong argument to be made that no general method can exist,
because it is, \eg, not possible to describe in general what is spurious information and what is relevant information.
Nevertheless, finding methods that are more generally applicable is a worthy goal.
